





\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}
\usepackage{array}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingtest}[4]{
  \vspace{-1pt}
   %  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \item \textbf{ #1} \hfill \small {#2} \\
      \textit{\small #3} \hfill \textit{\small #4} 
    % \end{tabular*}
    \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{center} 
  \textbf{{\huge Carrie (Jiayi) Lei}}  %\href{mailto:cjlei@ucdavis.edu}
   \end{center}
  \begin{tabular*}{\textwidth} {lll@{\extracolsep{\fill}}r}
  linkedin.com/in/jiayi-lei&   \quad \quad \quad  {github.com/UCDJLei}&\quad \quad \quad \quad {leoi06012015@gmail.com} &  (415)810-8610  \\

\end{tabular*}

\vspace{-10pt}


%-----------EDUCATION-----------------
\section{\textbf{Education}}

  \textbf{University of California, Davis} \hfill \small {GPA: 3.66} \\
      \textit{\small Bachelor of Science in \emph{\bf{Applied Mathematics}} with a Minor in \emph{\bf{Computer Science}}  } \hfill \textit{\small Jun. 2019} 


% \vspace{-15pt}
% -----------------Relative Classes ----------------------------
% \section{\small \textbf{Relevant Coursework}}
\small {Relevant Coursework:}
\vspace{-10pt}
% formatting
\begin{table}[!ht]
 \footnotesize	
 % \small
\begin{tabular}{ p{4.2cm}p{4.2cm}p{4.2cm}p{10cm}}


Applied Linear Algebra & Numerical Analysis 
 & Math for Data Analytics
&    Data Structure and Programming    \\
Computer Vision    &   Algorithm Design& Optimization   &    Object-Oriented Programming \\
  Financial Management & Principle of Statistics& Financial Accounting & Management Accounting\\

\end{tabular}

\end{table}
% \vspace{-20pt}
\vspace{-15pt}





%-----------EXPERIENCE-----------------
\section{\textbf{Work Experience}}
  \resumeSubHeadingListStart
  
   
   
    % 2
	\resumeSubheadingtest
    % \resumeSubheading
     {AP Computer Science Teaching Assistant}
      {Fremont}
      {IvyMax}
     {Sep. 2019 - Present}
      \resumeItemListStart
          \resumeItem{}
          {Create scenarios to test students' Java code to ensure the correctness of the code and debug code for students. }
        \resumeItem{}
          {Explain basic computer science concepts in ways that are easy for students to understand.}

  
      \resumeItemListEnd
   
   
  
  % 1
	\resumeSubheadingtest
    % \resumeSubheading
     {Hospital Corpsman, Petty Officer 3nd Class}
      {United State}
      {The United States Navy Reserve}
     {Jan 2017 - Present}
      \resumeItemListStart
          \resumeItem{}
          {Conduct preliminary physical examinations and provide emergency medical treatment. }
 
            \resumeItem{}
          {Communicate with medical providers and patients to provide professional medical assistance.}
  
      \resumeItemListEnd
      
      
       % 4 
    \resumeSubheadingtest
    {Math Lecture Note Reader and Editor}
      {Davis, CA}
      {UC Davis Math Department}
      {July. 2019 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Proofread lecture notes for class ``Math for Data Analytics and Decision Making'' in order to publish. }

          \resumeItem{}
          {Clarify and explain ambiguous content in order to make concept easier for students to understand.}
      \resumeItemListEnd
  
      
      
  
   % 5 
    
 
  
% 3
    \resumeSubheadingtest
     {Math Tutor}
      {Oakland, CA}
      {Math Lab Tutoring Center, Laney College}
     {Jan. 2016 - Dec. 2016}
      \resumeItemListStart
        \resumeItem{}
          {Provide private instruction to individuals and small groups of students in order to improve academic performance, occupational skills, and preparation for academic and occupational tests.
}
        \resumeItem{}
          {Teach students study skills, note-taking skills, and test-taking strategies.}
      \resumeItemListEnd
      

  \resumeSubHeadingListEnd


% \vspace{-5pt}

%-----------PROJECTS-----------------
\section{\textbf{Projects}}
  \resumeSubHeadingListStart
  
       
             
   \resumeSubItem{}
      {\emph{\bf{Breast Cancer Diagnose: }}Diagnose breast cancer by using Support Vector Machines (SVM) to analyze a dataset and build a mathematical model.}

      
      \resumeSubItem{}
    {\emph{\bf{Predict Survival on Titanic: }}Predict survival on the Titanic by using Logistic Regression in Scikit-learn, on a dataset that was cleaned by filling in missing data after analysis. Categorical features were converted by using pandas package.}
    
        \resumeSubItem{}
    {\emph{\bf{Classify California Census Data:}} Predict the income class of individuals from various features using the linear classification method in TensorFlow with an accuracy of 84\%. }
    
        \resumeSubItem{}
    {\emph{\bf{Monopoly: }}Implement Monopoly in C++ by using various concepts such as pointers, classes, inheritance etc.}
    
   
    
    

  


      
 
 
       \resumeSubItem{}
  {\emph{\bf{Visual Vocabulary}}: Build the visual vocabulary by using k-means method to cluster the scale-invariant feature transform (SIFT) descriptors of each images and use these visual vocabularies for image queries for similar content. } 
  
 
      
 
 \begin{comment}
 
  \resumeSubItem{}
 {\emph{\bf{Maximize Influence on Social Network: }} Present the friendship relationship of a Facebook social network as a graph and matrix, and find out the subgroup of users with maximum total influence restricted to certain user subgroup size.}
 
   \resumeSubItem{}
 {\emph{\bf{Text Mining:}}  Analyzed 180 papers from 20 scholars by counting the number of certain keywords in each document and converting the absolute numbers into relevant frequency by using the tf-idf formula and then clustering these papers using the Spectral Clustering.}
 
       \resumeSubItem{}
 {\emph{\bf{House Price Prediction:}} Present the data of house price, number of bedrooms and bathrooms by plotting them in a 3D graph and use the graph to analyze the relationship among them. Use linear regression and gradient descent method to train the house price prediction models.}
 
 
   

    \resumeSubItem{}
      {\emph{\bf{Spam Email Classification: }}Classify ``spam email" by using the LASSO mathematical model to extract most important information for a big set of data.}
      

    \resumeSubItem{}
      {\emph{\bf{Sudoku Solver: }}Automatically solve Sudoku puzzles by using ZIMPL.}
          \resumeSubItem{}
      {\emph{\bf{Visual Vocabulary Bank: }}Build visual vocabulary from a big set of images data bank and search for similar frames base on selected features or frames.} % Matlab
      
        

       \resumeSubItem{}
       {\emph{\bf{Mosaic: }}Create a mosaic from more than two pictures by computing the homography matrix and warping the images to the bigger frame.  }
      % Matlab
            
      
       \resumeSubItem{}
      {\emph{\bf{Handwritten Digits Classification: }}Classify handwritten digits by using singular value decomposition.}
      

      
      % project done in Introduction to Business class
      
      
      

\end{comment}    



    
  \resumeSubHeadingListEnd
  % text mining project implement later
  
  

%-----------Research Experience-----------------
\section{\textbf{Research Experience}}
  \resumeSubHeadingListStart

 \resumeSubheadingtest
      {Undergraduate Researcher}
     {Davis, CA}
      {UC Davis Math Department}
     {Jan. 2019 - Jun. 2019}
      \resumeItemListStart
            \resumeItem{}
           {Design and implement efficient algorithms to solve nonnegative Principal Component Analysis. }
        \resumeItem{}
        {Conduct numerical experiments for different algorithms and analyze the results.  }

       
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

  
 \section{\textbf{Skills}}
% \begin{tabular}{ @{} >{\bfseries} l p{5in} @{\hspace{4ex}} l }
\begin{tabular}{@{} >{\bfseries} p{5cm}p{15cm}}

Computer Languages & Python (TensorFlow, Scikit-learn), Java, C++, C, Matlab, ZIMPL, SQL \\
Other & git, \LaTeX, Active Secret Security Clearance, Microsoft 365, HIPPA, Enrolled Agent\\
Languages &  English, Mandarin, Cantonese\\


\end{tabular}
  
\section{\textbf{Honors and Awards}}
\resumeSubHeadingListStart
\resumeSubItem{}
      {Citation for Outstanding Performance from UC Davis Math Department. \hfill 2019}
      \resumeSubItem{}
      {Deans' Honor List Spring 2018, Winter 2019. \hfill 2018 - 2019}
      \resumeSubItem{}
      {Merit Award from the American Mathematical Association of Two-Year Colleges (AMATYC). \hfill 2015}

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
